### 2020-04-21 draft_ABP.tex
Updates from Overleaf

\section*{ABHY like realisation for the Permutahedron}
The following set of equations to define the $n$-dimensional Permutahedron: 
\bea
C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|}  X_I \right) \nonumber
\eea
for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.

It is clear that
\bea
m= \text{No. of  C's }&=& 2^{n+1}-(n+2) \nonumber \\
N= \text{No. of X's} &=& 2^{n+1}- 2 \nonumber 
\eea
Thus we see that $N= d+m$ as expected. We can write down the stringy integral as usual to be 
\bea
\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} d x_i x_i^{\alpha^{'} X_i -1} \prod_{I} \left (\sum_{a\in I} x_a \right) ^{-\alpha^{'} C_I} \nonumber
\eea 
where the product is over all non-singlets $ I \subset \{0,1,\cdots,n\}$ with $x_{0} =1$.

@@

The $u$-variables can be written in terms of $x$ variables as:
\bea
u_1&=&\frac{x(1+x+y)}{(x+y)(1+x)}, ~ u_2 =\frac{y(1+x+y)}{(x+y)(1+y)},~ u_{12}=\frac{(x+y)}{(1+x+y)}\nonumber \\
u^{'}_1&=&\frac{(1+y)}{(1+x+y)}, ~~~~~ u^{'}_2=\frac{(1+x)}{(1+x+y)},~~~~~ u^{'}_{12}= \frac{(1+x+y)}{(1+x)(1+y)} \nonumber
\eea
The $u$-equations are:
\bea
1-u_i &=& (u^{'}_i)^2 u_j u^{'}_{12}, ~~~ 1-u_{12} = u^{'}_{1} u^{'}_{2} u^{'}_{12} \nonumber \\
1-u^{'}_i &=& u_i u^{'}_j u_{12}, ~~~~~~~ 1-u^{'}_{12} = u_{1} u_{2} (u_{12})^2 \nonumber
\eea
where $i=1$ implies $j=2$ and vice versa.

@@

The $u$ and $u'$-variables can be written interms of $x$ variables as:
{\scriptsize  \bea
u_1&=&\frac{x(1+x+y)(1+x+z)(x+y+z)}{(x+y)(x+z)(1+x)(1+x+y+z)}, ~ u_2 =\frac{y(1+x+y)(1+y+z)(x+y+z)}{(x+y)(y+z)(1+y)(1+x+y+z)},~ u_{3}=\frac{z(1+x+z)(1+y+z)(x+y+z)}{(x+z)(y+z)(1+z)(1+x+y+z)},\nonumber \\
u^{'}_1&=&\frac{(1+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_2 =\frac{(1+x+z)}{(1+x+y+z)},~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{3}=\frac{(1+x+y)}{(1+x+y+z)},\nonumber \\
u_{12}&=&\frac{(x+y)(1+x+y+z)}{(1+x+y)(x+y+z)}, ~~~~~~~~~~~~~~~~~~ u_{23} =\frac{(y+z)(1+x+y+z)}{(1+y+z)(x+y+z)},~~~~~~~~~~~~~~~~~~~ u_{13}=\frac{(x+z)(1+x+y+z)}{(1+x+z)(x+y+z)},\nonumber \\
u^{'}_{12}&=&\frac{(1+z)(1+x+y+z)}{(1+y+z)(1+x+z)}, ~~~~~~~~~~~~~~~~~~ u^{'}_{23} =\frac{(1+x)(1+x+y+z)}{(1+x+y)(1+x+z)},~~~~~~~~~~~~~~~~~~~ u^{'}_{13}=\frac{(1+y)(1+x+y+z)}{(1+x+y))(1+y+z)},\nonumber  \\
u_{123}&=&\frac{(x+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{123} =\frac{(1+x+y)(1+y+z)}{(1+x)(1+y)(1+z)(1+x+y+z)}\nonumber
\eea }
The $u$-equations in this case are:
{\small  \bea
1-u_i &=& u_j u_k (u_{jk})^2 (u^{'}_i)^3 (u^{'}_{ij})^2(u^{'}_{ik})^2 u^{'}_{123} \left(1+ u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}\right), ~~ 1-u_{ij} = u_k u_{ik} u_{jk} (u^{'}_i)^2 (u^{'}_{j})^2 (u^{'}_{ij})^2 u^{'}_{ik} u^{'}_{jk} u^{'}_{123} \nonumber  \\
1-u^{'}_i &=& u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 1-u^{'}_{ij} = u_i u_{j}  (u_{ij})^2 u_{ik} u_{jk} (u_{123})^2 (u^{'}_{k})^2 u^{'}_{ik} u^{'}_{jk}  \nonumber \\
1-u^{'}_{123} &=& u_1 u_{2} u_{3} (u_{12})^2 (u_{23})^2  (u_{13})^2 (u_{123})^3 \left(1+ u^{'}_{123}  u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} \right), 1-u_{123} = u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} u^{'}_{123}   \nonumber
\eea}
where $i,j,k \in {1,2,3}$ and $i \neq j \neq k$.

The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u^{'}_i \rightarrow 0,u_{123} \rightarrow 0 ~and ~u^{'}_{123} \rightarrow 0$  are all $B_2$'s. Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u^{'}_{ij} \rightarrow 0$ are all  $A^{2}_1$.

@@

In this section we shall try to argue that the permutahedron is a binary geometry. We shall first summarise the following facts about the permutahedron:
\begin{enumerate}
\item The $u$-variables for the permutahedron are: 
\bea
u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber 
\eea
The above relations can also be inverted to obtain $x_I$ as follows:

The above  follows directly from the following relations amongst $u$ for each $I$ such that $0\notin I$ :
\bea
1-\prod_{I \subset J} u_{J} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}} \\
1-\prod_{J \subset I} u_{\bar{J}} &=& \prod_{I \subset J} u_{J} \prod_{J \subset \bar{I} } u_{\bar{J}}
\eea

% Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.

\item  Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and this is indeed the case as $u_I$ with the same $|I|$ have similar $u$'s. i.e $u_J$ can be obtained from $u_I$ for $|J|=|I|$ by interchange of some of the $x_i$'s.

@@

\end{enumerate}

\section*{Permutahedron}
 For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron $P_n(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
 \bea
 P_n(x_1,x_2, \cdots, x_{n+1}) = ConvexHull \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
 \eea
 where $S_{n+1}$ is the symmetric group.

 The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
 \bea
 H_c= \{(t_1,t_2, \cdots, t_{n+1}) | t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
 \eea
where $c= x_1+x_2+ \cdots +x_{n+1}$

For $n=2$ and distinct $x_1,x_2, x_3$ the permutahedron $P_2(x_1,x_2, x_3)$ is a hexagon. If two of the $x_i$'s are equal then the permutahedron degenerates into a triangle and if $x_1= x_2 = x_3$ then its degenerates into a single point.

We shall state a few results about permutahedra:

{\bf Rado's theorem}: For any $x_1 \ge x_2  \cdots \ge x_{n+1}$ a point $(t_1,t_2, \cdots, t_{n+1}) \in \mathbb{R}^{n+1}$ belongs to the permutahedron $P_n(t_1,t_2, \cdots, t_{n+1})$ if and only if 
\bea
t_1+ \cdots +t_{n+1} = x_1 +\cdots+ x_{n+1} \nonumber
\eea
and for any nonemepty subset $\{i_1,\cdots,i_k \} \subset \{1,\cdots, n+1 \}$, we have 
\bea
t_{i_1}+ \cdots +t_{i_k} \leq x_1 +\cdots+ x_k \nonumber
\eea
The combinatorial structure of the permutahedron $P_n (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct.

{\bf Proposition 2}: For any  $x_1> \cdots > x_{n+1} $. The $d$-dimensional faces of $P_n ( x_1, \cdots, x_{n+1 })$ are in one-to-one correspondence with the disjoint subdivisions of the corresponding set $\{x_1,\cdots, x_{n+1 }\}$ into nonempty ordered blocks $B_1 \cup B_2 \cup \cdots \cup B_{n+1-d} =\{1,\cdots,n+1 \}$. The face corresponding to $B_1,\cdots, B_{n+1-d}$ is given by the $n+1-d$ linear equations 
\bea
\sum_{i \in B_1\cup \cdots \cup B_k} t_i = x_1 + \cdots +x_{| B_1 \cup \cdots \cup B_k |}, ~~~ for~ k=1,\cdots,n+1-d \nonumber
\eea 
\section*{Generalized permutahedra}
Generalized permutahedra are polytopes which are deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved though some of the edges may degenerate into points.

 Since each generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [n+1] := \{1,\cdots,n+1 \}$
 \bea
 P_n^z(\{ z_I \}) = \left \{ (t_1, t_2, \cdots , t_{n+1}) \in \mathbb{R}^{n+1} | \sum_{i=1}^{n+1} t_i = z_{[n+1]},~ \sum_{i \in I} t_i \geq z_I, ~for ~subsets~ I  \right  \} \nonumber
 \eea

 If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron.

 A different construction of the generalised permutahedron is the following :

 Let, $\Delta_{[n+1]} = ConvexHull(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. For any $I \subset [n+1] $ let $\Delta_I =ConvexHull(e_i~|~i\in I)$ denote the face of the $\Delta_{[n+1]}$. The polytope $P_n^y(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I \geq 0$ for all nonempty subsets $I \subset [n+1]$
 \bea
 P_n^y(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  \nonumber
 \eea
is the generalised permutahedron $P_n^z(\{z_I \})$  provided $z_I = \sum_{J \subset I} y_J  ~ for ~all~nonempty ~I \subset [n+1]$.
Note that all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices and we shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation.
\section*{Nested Complex}
Since the combinatorial structure of the generalised permutahedron depends only on the set $B$ of nonemepty subsets $I \subset [n+1]$ such that $y_I \geq 0$ which is called the {\it building set}. We can describe the combinatorial structure when $B$ additionally satisfies the following:

\noindent(1) If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$. \\
(2) $B$ contains all singletons $\{ i\}$ for $i \in S$.

A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:\\
\noindent
(1) For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.\\
(2) For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B. \\
(3) N contains all maximal elements of $B$.

The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.

{\bf Theorem 1}: Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[n+1]$. Then the poset of faces $P_n^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.

{\bf Theorem 2}: Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[n+1]$. The face $P_N$ of $P_n^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is given by:
\bea
P_N = \left \{ \right (t_1,\cdots,t_{n+1}) \in \mathbb{R}^{n+1} | \sum_{i \in I} t_i =y_{I}~for~I \in N; ~ \sum_{i \in J}t_i \geq y_J, for J \in B  )\}
\eea
In particular the dimension of the face $P_N$ equals $n+1-|N|$.

In summary the above results imply that we can look at any collection of subsets of $[n+1]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set. Further, the number of facets of the generalised permutahedron just correspond to the set of all non-singlet elements in $B$.  
We shall use $ \{0,1,\cdots,n \}$ instead of $[n+1]$ with $x_0 =1$ from now on. Since, the number of singlets correspond to the dimension of the generalised permutahedron this implies that:

{\bf Number of facets = Number of linear equation + dimension of  gen permutahedron}

Thus, generalised permutahedra have "Big Polytope" which correspond to a simplex and we can write down the stringy canonical forms and solve for the $u$-variables and examine if they satisfy some kind of $u$-equations.

(1) If $B$ consists of only singlets i.e., $B=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex. In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ and $\sum_{i=0}^n x_i$. 
The Newton polytope of the Minkowski sum is $\prod_{i=1}^{n} x_i (1+\sum_{j=1}^{n} x_j)$ and $u$-variables are 
$u_i =\frac{ x_i}{1+\sum_{i=1}^n x_i} $
which satisfy $\sum u_i =1$ as their only $u$-equation. \\

(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then $P_n({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
$u_i =\frac{ 1}{1+\sum_{j=1}^{i} x_j} $, ~~$u^{'}_i =\frac{ \sum_{j=1}^{i} x_j}{1+\sum_{j=1}^{i} x_j} $ for $j=1,\cdots,n$ \\
which satisfy $u_i +u^{'}_{i} =1$ as their $u$-equation. \\

(3) If $B$ corresponds to all the non empty subsets of $\{0,1,\cdots,n \}$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then $P_n({\bf Y})$ is the usual permutahedron $P_n$.

\section*{ABHY like realisation for the Permutahedron}
The following set of equations to define the $n$-dimensional Permutahedron: 
\bea
C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|}  X_I \right) \nonumber
\eea
for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.

It is clear that
\bea
m= \text{No. of  C's }&=& 2^{n+1}-(n+2) \nonumber \\
N= \text{No. of X's} &=& 2^{n+1}- 2 \nonumber 
\eea
Thus we see that $N= d+m$ and hence the "Big polytope" in this case is again a simplex. We can write down the stringy integral as usual to be 
\bea
\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} d x_i x_i^{\alpha^{'} X_i -1} \prod_{I} \left (\sum_{a\in I} x_a \right) ^{-\alpha^{'} C_I} \nonumber
\eea 
where the product is over all non-singlets $ I \subset \{0,1,\cdots,n\}$ with $x_{0} =1$.

We can then solve for the corresponding $u's$ :
\bea
u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+\color{red}{mod(n, 2)}}} \nonumber
\eea

The $u$-variables can be written in terms of $x$ variables as:
\bea
u_1&=&\frac{x(1+x+y)}{(x+y)(1+x)}, ~ u_2 =\frac{y(1+x+y)}{(x+y)(1+y)},~ u_{12}=\frac{(x+y)}{(1+x+y)}\nonumber \\
u^{'}_1&=&\frac{(1+y)}{(1+x+y)}, ~~~~~ u^{'}_2=\frac{(1+x)}{(1+x+y)},~~~~~ u^{'}_{12}= \frac{(1+x+y)}{(1+x)(1+y)} \nonumber
\eea
The $u$-equations are:
\bea
1-u_i &=& (u^{'}_i)^2 u_j u^{'}_{12}, ~~~ 1-u_{12} = u^{'}_{1} u^{'}_{2} u^{'}_{12} \nonumber \\
1-u^{'}_i &=& u_i u^{'}_j u_{12}, ~~~~~~~ 1-u^{'}_{12} = u_{1} u_{2} (u_{12})^2 \nonumber
\eea
where $i=1$ implies $j=2$ and vice versa.
Let us look at the $n=3$ example.

The $u$ and $u'$-variables can be written interms of $x$ variables as:
{\scriptsize  \bea
u_1&=&\frac{x(1+x+y)(1+x+z)(x+y+z)}{(x+y)(x+z)(1+x)(1+x+y+z)}, ~ u_2 =\frac{y(1+x+y)(1+y+z)(x+y+z)}{(x+y)(y+z)(1+y)(1+x+y+z)},~ u_{3}=\frac{z(1+x+z)(1+y+z)(x+y+z)}{(x+z)(y+z)(1+z)(1+x+y+z)},\nonumber \\
u^{'}_1&=&\frac{(1+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_2 =\frac{(1+x+z)}{(1+x+y+z)},~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{3}=\frac{(1+x+y)}{(1+x+y+z)},\nonumber \\
u_{12}&=&\frac{(x+y)(1+x+y+z)}{(1+x+y)(x+y+z)}, ~~~~~~~~~~~~~~~~~~ u_{23} =\frac{(y+z)(1+x+y+z)}{(1+y+z)(x+y+z)},~~~~~~~~~~~~~~~~~~~ u_{13}=\frac{(x+z)(1+x+y+z)}{(1+x+z)(x+y+z)},\nonumber \\
u^{'}_{12}&=&\frac{(1+z)(1+x+y+z)}{(1+y+z)(1+x+z)}, ~~~~~~~~~~~~~~~~~~ u^{'}_{23} =\frac{(1+x)(1+x+y+z)}{(1+x+y)(1+x+z)},~~~~~~~~~~~~~~~~~~~ u^{'}_{13}=\frac{(1+y)(1+x+y+z)}{(1+x+y))(1+y+z)},\nonumber  \\
u_{123}&=&\frac{(x+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{123} =\frac{(1+x+y)(1+y+z)}{(1+x)(1+y)(1+z)(1+x+y+z)}\nonumber
\eea }
The $u$-equations in this case are:
{\small  \bea
1-u_i &=& u_j u_k (u_{jk})^2 (u^{'}_i)^3 (u^{'}_{ij})^2(u^{'}_{ik})^2 u^{'}_{123} \left(1+ u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}\right), ~~ 1-u_{ij} = u_k u_{ik} u_{jk} (u^{'}_i)^2 (u^{'}_{j})^2 (u^{'}_{ij})^2 u^{'}_{ik} u^{'}_{jk} u^{'}_{123} \nonumber  \\
1-u^{'}_i &=& u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 1-u^{'}_{ij} = u_i u_{j}  (u_{ij})^2 u_{ik} u_{jk} (u_{123})^2 (u^{'}_{k})^2 u^{'}_{ik} u^{'}_{jk}  \nonumber \\
1-u^{'}_{123} &=& u_1 u_{2} u_{3} (u_{12})^2 (u_{23})^2  (u_{13})^2 (u_{123})^3 \left(1+ u^{'}_{123}  u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} \right), 1-u_{123} = u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} u^{'}_{123}   \nonumber
\eea}
where $i,j,k \in {1,2,3}$ and $i \neq j \neq k$.

The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u^{'}_i \rightarrow 0,u_{123} \rightarrow 0 ~and ~u^{'}_{123} \rightarrow 0$  are all $B_2$'s. Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u^{'}_{ij} \rightarrow 0$ are all  $A^{2}_1$.

Thus, the 3d permutahedron integral factorizes nicely on all massless poles at finite $\alpha^{'}$ !!

@@

\section*{Associahedra}
If $B=\{ \{i,i+1,\cdots,j \} | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then $P_n({\bf Y})$ is the associahedron .
\section*{2d associahedron as generalized permutahedron}
In this case the building set $B=\{ \{ 0,1,2\},\{ 0,1\},\{1,2\},\{0\},\{1\},\{2\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_{01}=1+x,~ x_{12}=x+y,~ x_{012}=1+x+y$.

We can write down the Newton polynomial for the Minkowski sum as $ x_1~ x_2~(1+x_1)~(x_1+x_2)~(1+x_1+x_2)$.

The $u$-variables can be written in terms of $x$ variables as:
\bea
u_1=\frac{x
   (x+y+1)}{(x+1)
   (x+y)},u_2=\frac{x +y}
   {x+y+1},u_3=\frac{y}{x+y},u_4=\frac{x+1}{x+y+1},u_5=\frac{1}{x+1} \nonumber
\eea
The $u$-equations are:
\bea
1-u_1=u_3 u_5,1-u_2=u_4
   u_5,1-u_3=u_1 u_4,1-u_4=u_2
   u_3,1-u_5=u_1 u_2 \nonumber
\eea
Notice that these are precisely the $u$ equations for the ABHY realisation of $A_2$.
\section*{3d associahedron as generalized permutahedron}
In this case the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{1,2,3\},\{0,1\},\{1,2\},\{2,3\},\{0\},\{1\},\{2\},\{3\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y,~x_3 =y, ~x_{01}=1+x,~ x_{12}=x+y,~x_{23}=y+z,~ x_{012}=1+x+y,~ x_{123}=x+y+z,~ x_{0123}=1+x+y+z$.

We can write down the Newton polynomial for the Minkowski sum as $ x_1~ x_2~x_3~(1+x_1)~(x_1+x_2)~(x_2+x_3)~(1+x_1+x_2)~(x_1+x_2+x_3)~(1+x_1+x_2+x_3)$. \\

The $u$-variables can be written in terms of $x$ variables as:
{\scriptsize \bea
u_1&=&\frac{x
   (x+y+1)}{(x+1)
   (x+y)},~u_2=\frac{(x+y
   )
   (x+y+ z+1)}{(x+y+1)
   (x+ y+z)},~u_3=\frac{x+
   y+ z}{x+y+z +1},~u_4=
   \frac{y}{x+z},\nonumber \\ u_5&=&\frac{
   y
   (x+y+z)}{(x+y)
   (y+z)},~u_6= \frac{y+z}
   {x+y+z},u_7=\frac{x+y+1}{x+y+z+1},u_8=\frac{x+1}{x+y+1},u_9=\frac{
   1}{x+1} \nonumber
   \eea}
   and satisfy the $u$-equations 
   \bea
   1-u_1&=&u_5 u_6 u_9,~1-u_2=u_4
   u_6 u_8 u_9,~1-u_3=u_7 u_8
   u_9,~1-u_4=u_2 u_5 u_7, \nonumber \\ 1-u_5&=&u_1
   u_4 u_8,1-u_6=u_1 u_2 u_7
   u_8,1-u_7=u_3 u_4 u_6,1-u_8=u_2
   u_3 u_5 u_6,1-u_9=u_1 u_2
   u_3 \nonumber
   \eea
  We see again that these are precisely the $u$ equations of ABHY realisation of $A_3$ !

This is not a coincidence and it extends to all $n$ since the corresponding Newton polytope is given by $\prod_{1\leq  i \leq j \leq n} (x_i +x_{i+1}+\cdots+x_j)$ is nothing but the Loday's realisation of the associahedron which is equivalent to the ABHY type $A_n$ associahedron.

>>>>

\section*{ABHY like realisation for the Permutahedron}
The following set of equations to define the $n$-dimensional Permutahedron: 
\bea
C_I = (-1)^{|I|} \left( \sum_{i \in I} F_i - \sum _{{i<j}\atop{i,j \in I}} F_{ij} +\cdots + (-1)^{|I|}  F_I \right) \nonumber
\eea
for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $F_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.

It is clear that
\bea
m= \text{No. of  C's }&=& 2^{n+1}-(n+2) \nonumber \\
N= \text{No. of F's} &=& 2^{n+1}- 2 \nonumber 
\eea
Thus we see that $N= d+m$ as expected. We can write down the stringy integral as usual to be 
\bea
\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} d x_i x_i^{\alpha^{'} F_i -1} \prod_{I} \left (\sum_{a\in I} x_a \right) ^{-\alpha^{'} C_I} \nonumber
\eea 
where the product is over all non-singlets $ I \subset \{0,1,\cdots,n\}$ with $x_{0} =1$.

@@

The $u$-variables can be written in terms of $x$ variables as:
\bea
u_1&=&\frac{x(1+x+y)}{(x+y)(1+x)}, ~ u_2 =\frac{y(1+x+y)}{(x+y)(1+y)},~ u_{12}=\frac{(x+y)}{(1+x+y)}\nonumber \\
u_{02}&=&\frac{(1+y)}{(1+x+y)}, ~~~~~ u_{01}=\frac{(1+x)}{(1+x+y)},~~~~~ u_{0}= \frac{(1+x+y)}{(1+x)(1+y)} \nonumber
\eea
The $u$-equations are:
\bea
1-u_i &=& (u_{0j})^2 u_j u_{0}, ~~~ 1-u_{12} = u_{02} u_{01} u_{0} \nonumber \\
1-u_{0 j} &=& u_i u_{0 i} u_{12}, ~~~~~~~ 1-u_{0} = u_{1} u_{2} (u_{12})^2 \nonumber
\eea
where $i=1$ implies $j=2$ and vice versa.

@@

The $u$ and $u'$-variables can be written interms of $x$ variables as:
{\scriptsize  \bea
u_1&=&\frac{x(1+x+y)(1+x+z)(x+y+z)}{(x+y)(x+z)(1+x)(1+x+y+z)}, ~ u_2 =\frac{y(1+x+y)(1+y+z)(x+y+z)}{(x+y)(y+z)(1+y)(1+x+y+z)},~ u_{3}=\frac{z(1+x+z)(1+y+z)(x+y+z)}{(x+z)(y+z)(1+z)(1+x+y+z)},\nonumber \\
u_{023}&=&\frac{(1+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{013} =\frac{(1+x+z)}{(1+x+y+z)},~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{012}=\frac{(1+x+y)}{(1+x+y+z)},\nonumber \\
u_{12}&=&\frac{(x+y)(1+x+y+z)}{(1+x+y)(x+y+z)}, ~~~~~~~~~~~~~~~~~~ u_{23} =\frac{(y+z)(1+x+y+z)}{(1+y+z)(x+y+z)},~~~~~~~~~~~~~~~~~~~ u_{13}=\frac{(x+z)(1+x+y+z)}{(1+x+z)(x+y+z)},\nonumber \\
u_{03}&=&\frac{(1+z)(1+x+y+z)}{(1+y+z)(1+x+z)}, ~~~~~~~~~~~~~~~~~~ u_{01} =\frac{(1+x)(1+x+y+z)}{(1+x+y)(1+x+z)},~~~~~~~~~~~~~~~~~~~ u_{02}=\frac{(1+y)(1+x+y+z)}{(1+x+y))(1+y+z)},\nonumber  \\
u_{123}&=&\frac{(x+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{0} =\frac{(1+x+y)(1+y+z)}{(1+x)(1+y)(1+z)(1+x+y+z)}\nonumber
\eea }
The $u$-equations in this case are:
{\small  \bea
1-u_i &=& u_j u_k (u_{jk})^2 (u_{0jk})^3 (u_{0k})^2(u_{0 j})^2 u_{0} \left(1+ u_i u_{ij} u_{ik} u_{0ik} u^_{0ij}  u_{0i}\right),  1-u_{ij} = u_k u_{ik} u_{jk} (u_{0jk})^2 (u_{0ik})^2 (u_{0 k})^2 u_{0 j} u_{0 i} u_{0} \nonumber  \\
1-u_{0 j k} &=& u_i u_{ij} u_{ik} u_{0 i k} u_{0 i j}  u_{0 i}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 1-u_{0 k} = u_i u_{j}  (u_{ij})^2 u_{ik} u_{jk} (u_{123})^2 (u_{0 i j})^2 u_{0 j} u_{0 i}  \nonumber \\
1-u_{0} &=& u_1 u_{2} u_{3} (u_{12})^2 (u_{23})^2  (u_{13})^2 (u_{123})^3 \left(1+ u_{0}  u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} \right), 1-u_{123} = u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} u_{0}   \nonumber
\eea}
where $i,j,k \in {1,2,3}$ and $i \neq j \neq k$.

The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u_{0jk} \rightarrow 0,u_{123} \rightarrow 0 ~and ~u_{0} \rightarrow 0$  are all $B_2$'s. Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u_{0k} \rightarrow 0$ are all  $A^{2}_1$.

@@

In this section we shall try to argue that the permutahedron is a binary geometry.

Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and this is indeed the case as $u_I$ with the same $|I|$ have similar $u$'s. i.e $u_J$ can be obtained from $u_I$ for $|J|=|I|$ by interchange of some of the $x_i$'s.

@@

\section*{A degeneration of ${\mathescr P_n}$ with perfect $u$-equations}
We can also consider general Minkowski sums of non-simplices and see if these also give us any instance of polytopes with perfect $u$ equations. One such case is the following:

There are exactly $n-3$ $u$'s which have $1-u$ is product of 4 u's:
\bea
1-u_{n+3} =u_{n} u_{n+2}u_{n+5} u_{3n-1} ~~and~~
1-u_{n+5+ 2 i} =u_{n-3-i} u_{n+3+2 i} u_{n+4+2 i} u_{n+7+2 i}~ for~i=0,\cdots,(n-5) \nonumber 
\eea
It would be nice to see if these also correspond to some degeneration of the associahedron or if they  are generalised permutahedra.

\newpage
\section{Discussions}
There are several interesting open questions, like the question of  whether degenerations of other cluster types (in particular $C_n$ and $D_n$ can also give binary geometries with (perfect?) $u$-equations.\\\\
\noindent
Though many examples of degenerations of $A_n$ and $B_n$ were products of lower dimensional objects of the same type, there were examples where we got non-trivial degenerations which did not factor. We would like to completely classify these cases and this would settle the question of identifying all the ``atoms'' of binary geometries with perfect $u$-equations. One class of examples which is certainly of both mathematical and physical interest in this context are the Stokes polytopes (and more generally Accordiohedra).

\section{Appendix}

@@

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{utphys}
\bibliography{final}
\end{document}
